\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-30 paper.qmd
Update the S-curve true model with data figure
Update figure for prediction

Three views of the true model in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/bcQg4XcRjhc>). 
:::

@@

<!--To generate prediction for true-model of S-curve-->
```{r}
true_model_df <- read_rds("data/s_curve/true_model.rds")
true_model_df <- true_model_df |>
  mutate(ID = row_number())

training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")

## To initialize effective bins along x
effective_bin1_scurve <- 12

true_pred_df <- predict_emb(
  test_data = true_model_df, 
  df_bin_centroids = df_bin_centroids_scurve, 
  df_bin = df_bin_scurve, 
  type_NLDR = "UMAP"
  )

true_pred_df |>
    ggplot(aes(x = pred_UMAP_1,
               y = pred_UMAP_2)) +
    geom_point(
      alpha=0.5,
      color = "#33a02c"
      )
```

>>>>

Three views of the true model in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/tYATMiSlCXQ>). 
:::

@@

<!--prediction for true-model of S-curve-->
::: {#fig-scurve-pred-sc layout-ncol="2" fig-pos="H"}
![](figures/scurve/sc_true_only.png)

![](figures/scurve/pred_true_view.png)

A view of the true model in projections from $7\text{-}D$, and predictions of the true model in \gD{}, for the S-curve data. The predictions fits the UMAP layout which means that it capture the geometry of S-curve with UMAP.
:::

### 2024-06-30 paper.tex
Update the S-curve true model with data figure
Update figure for prediction

\caption{\label{fig-scurve-true-sc}Three views of the true model in
projections from \(7\text{-}D\), for the S-curve data. The model closely
fits the shape. (The \textbf{langevitour} software is used to view the
data with a tour, and the full video is available at
(\url{https://youtu.be/bcQg4XcRjhc}).}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-15-1.pdf}
\end{center}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-32-1.pdf}

>>>>

\caption{\label{fig-scurve-true-sc}Three views of the true model in
projections from \(7\text{-}D\), for the S-curve data. The model closely
fits the shape. (The \textbf{langevitour} software is used to view the
data with a tour, and the full video is available at
(\url{https://youtu.be/tYATMiSlCXQ}).}

@@

\begin{minipage}{0.50\linewidth}
\includegraphics{figures/scurve/sc_true_only.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/scurve/pred_true_view.png}\end{minipage}%

\caption{\label{fig-scurve-pred-sc}A view of the true model in
projections from \(7\text{-}D\), and predictions of the true model in
\gD{}, for the S-curve data. The predictions fits the UMAP layout which
means that it capture the geometry of S-curve with UMAP.}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-31-1.pdf}
